---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# corpoaccidentdash

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![License: MIT](https://img.shields.io/badge/License-MIT-blue.svg)](https://opensource.org/licenses/MIT)
[![GitHub commit](https://img.shields.io/github/last-commit/ngsanogo/corpoaccidentdash)](https://github.com/ngsanogo/corpoaccidentdash/commit/master)
<!-- badges: end -->

This accident dashboard provides an overview of traffic accidents involving injuries in France from 2005 to 2018.
This dashboard is built with R using the package `golem` and can easily reproduce by others.

The data behind this dashboard can be found in the [following repository](https://github.com/ngsanogo/corpoaccident).

## Installation

You can install corpoaccidentdash from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("ngsanogo/corpoaccidentdash")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval=FALSE}
library(corpoaccidentdash)
## basic example code
run_app()
```

## Code of Conduct
  
  Please note that the corpoaccidentdash project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
